\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Working hard

\subsection{The $n$ Ambulance Problem}

\subsubsection{$n=3$ Problem}

\subsubsection{$n=2$ Problem}

\subsubsection{$n=1$ Problem}

>>>>

\subsection{The $n$ Ambulance Problem}
With the $n$ ambulance problem, we are trying to figure out where to place each of the $n$ ambulances so that the reach of each ambulance covers the most amount of people. For our purposes, this reach is solely determined by how far the ambulance can travel in an eight minute span.

With the given county, made up of six zones, we consider the location optimization under three scenarios; with three ambulances, with two ambulances, and finally, with one ambulance. Our goal is to see a) if we can cover everybody in the county in an eight minute span, and b) if not, how many people are we failing to cover.

The number of people the ambulances are able to cover is a function of our population density function, while the actual location optimization is done by our greedy optimizer.

\subsubsection{$n=3$}

\subsubsection{$n=2$}

\subsubsection{$n=1$}
